CTest Integration of Sikuli Automated GUI Testing

### 2011-06-09 Documentation/Article.tex
It now compiles
Add references

% Personal settings for code snippets visualization
\input{settings/TexCodeSet}

@@

@@

% Feel free to change section titles
\subsection{What is sikuli?}
Sikuli is a programming language that uses screen shot images as variables
and objects in order to automate graphical user interface functions. The
Sikuli program is comprised of an IDE where the user can write scripts that 
include screen shot thumbnails so they can visually track the functions of
their code. The Sikuli Script is built on a Jython (Python for Java platform)
library which uses Python syntax in addition to a number of special Sikuli
functions for aquiring and handling screenshot images and performing mouse,
keyboard actions, the most useful of which are conveniently found as buttons
on the Sikuli IDE.  Sikuli then saves a script in a directory with a unique
extension .sikuli.  The directory consists of a the Sikuli script file in a 
html file and as well as a Python script file and includes a list of all the 
screenshot images used in the script.

@@

\begin{figure}[htp]
 \centering

 \caption{here is my caption}
 \label{fig:SimpleExample}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{InsightJournal,AntoBib}

>>>>

@@

\usepackage{url}

@@

% Feel free to change section titles
\subsection{What is sikuli?}

Sikuli~\cite{Sikuli:Documentation,Sikuli:Website,Yeh:2009:Sikuli} is a visual
technology to automate and test graphical user interfaces (GUI) using images
(screenshots). Sikuli includes \emph{Sikuli Script} and \emph{Sikuli IDE}.\\

\emph{Sikuli Script} automates anything you see on the screen without internal
API's support. Sikuli Script is a programming language that uses screen shot
images as variables and objects in order to automate graphical user interface
functions. The Sikuli Script is built on a Jython (Python for Java platform)
library which uses Python syntax in addition to a number of special Sikuli
functions for acquiring and handling screen shot images and performing mouse,
keyboard actions.\\

In the \emph{Sikuli IDE}, the user can write scripts that include screen shot
thumbnails so they can visually track the functions of their code. The most
useful functions from Sikuli scripts are conveniently found as
buttons on the IDE. When using the IDE, Sikuli then saves a script in a
directory with a unique extension .sikuli. The directory consists of a python
script file (script file to be used by sikuli), an html file, and a list of all
the screenshot images used in the script.

@@

\begin{figure}[htp]
 \centering
 \caption{here is my caption}
 \label{fig:SimpleExample}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{InsightJournal,biblio}
